Differential invariant signatures for planar Lie group transformations of images

### 2020-11-18 paper/newpaper.tex
All lit

\section{Introduction}
\todo[inline]{
Literature
Discussion -- syzygies

Sim(2) by contraction
A(2) by transvectant
Check signatures for Mobius etc.
}

The appearance of a fixed object in a set of images can vary markedly depending upon such variables as pose and position relative to the camera, even though the object itself does not change. This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera and any fixed background. The appearance of each individual object will then vary independently as a constant camera motion or other such transformation is applied. Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.

@@

Classical invariants

>>>>

\section{Introduction}
The appearance of a fixed object in a set of images can vary markedly depending upon such variables as pose and position relative to the camera, even though the object itself does not change. This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera and any fixed background. The appearance of each individual object will then vary independently as a constant camera motion or other such transformation is applied. Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.

@@
